Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-04 doc/main_jfm.tex
adding some texts

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
\end{center}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the intergal equation method.
  }
    \label{figure1}
\end{figure}

@@

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
\end{center}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the result from the integral equation method.
  }
    \label{figure1}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.4\textwidth]{N58_0.eps}
\includegraphics[width=0.4\textwidth]{N58_20000.eps}
\end{center}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
  }
    \label{figure2}
\end{figure}
